%! program = pdflatex

%\documentclass[12pt,a4paper]{memoir} % for a long document
\documentclass[12pt,a4paper,article]{memoir} % for a short document

% See the ``Memoir customise'' template for some common customisations
% Don't forget to read the Memoir manual: memman.pdf
\usepackage{paralist}
\title{Medical School Interview}
\author{Fernando Ramirez}
\date{} % Delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\maketitle
\tableofcontents* % the asterisk means that the contents itself isn't put into the ToC

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Important Questions}
1) Why do you want to be a doctor? Looking for passion in medicine and why you want to become a physcian.
Top Three Reasons:
	I want to provide care to the underprivileged families in Texas.  One of the key factors that people have to have in order to succeed is their health and as an individual who gets a lot of joy from empowering people, I feel that one of the ways that I can give back to society is by giving people their health back.  
	I know from experience that a health emergencies can often start poverty cycles.  I grew up underprivileged saw the difficulties one has to overcome to be successful, and was inspired by resources organizations such as free clinics and medicare provided to the lower class.  
	As a physician I want to provide quality healthcare at an affordable price, by reducing my own salary.  As nieve as that sounds, there are articles be reputable news magazines such as forbes that support the idea that physicians in the United States are overpaid to begin with. 

2)Where do you want to be in 10 years?  Have you thought about your career goals and what type of interest do  you have in your own future
2 years of undergrad left
6 years of medical school and residency or 6 years of grad school getting a Ph.D (optimistic estimate)
2 years into my career, as a Practicing physician or a general surgeon, with an interest in the presentation of medical data to patients.  In an increasingly digital world I think that it is safe to say that by the time I complete medical school the game will have changed a little bit and I would like to think that things as vital as medical charts and blood records become more personally useful and less medical garçon.  I would like to be on the front end of that train with experience with low level programming in apps. 
In my personal life I plan to be married and perhaps even have a child.  I would like to be involved in charitable organizations and lead an active lifestyle with my wife, but we will see how the active part plays out.  

3)What do you want to specialize in? Open ended question where the interviewer is looking to see what you plan to do in the field of medicine.
There is one reason I would choose not to specialize and the first is the need for primary care physicians and general surgeons in our society.  Lots of very smart and talented physicians are choosing to specialize for lucrative and academic purposes, there is the fact that as you get experience in a field that interest you you tend to specialize in that field.  There is evidence to suggest that an increase in these specialized   If I were to specialize in a field, it would be cardiology.  There is a very particular interest I have with the romantic image of the heart, its strength, and the rise in heart related deaths due to a rise in obesity and other factors in our society.

4)What are your 2 best points? Whats to see if the applicant has some insight into our greatest strengths and weaknesses
My two best points are the respect I give others and my dedication to help people live successful full lives.  I look around at the opportunities I have had, the ideas presented in Malcolm Gladwells Outliers, and I see the great fortune that I have had in getting to where I am today.  The opportunities I have had and taken.  The people I have met and helped me.  And I see how I can be that person to somebody out there.  My goal in life has never been to fix the world.  That would take an army.  but instead to influence as many people as I can in a positive light so as to make their life better, whether it be a talk given at a high school, some mentoring lunches, or a simple smile between strangers frossing the street.  Whatever way I can make the life of another human being better in this world I will do it.  Note: Sounds a little preachy.  

5)What are your 2 weakest points?
I am very stubborn and often very proud.  
One of my weaknesses i that I have a hard time relaying my ideas in words when working in teams I prefer to use other methods such as power points or just written messages to convey what I feel.  Another weakness is that I am very introverted.  I love working in complete silence and often solitude and feel I work best in an environment where I have complete control.
I also have trouble communicating ideas orally.  

6)Tell me about yourself. Present the positive things about me and present some of the adversities that i have overcome to be where I am and helped me be who I am.
I am a first generation college student. I come from a home of 7. My parents were both immigrants from Mexico, my dad a citizen, my mom a legal resident.  Thanks to my parents belief in educeatoin, and my own desire to be successful I did really well in my early grade school years, which set me up for academic success in high school, which has me studying at Rice University now, studying bioengineering with the the desire to become a physician.  Times weren't always easy growing up, and they still aren't. I started working at the age of 15 to bring additional income into the house and cover some of the expenses that school brought with it. I tried saving for a car several times as most teenagers with a job usually do, but things like school and the occasional house expense would always keep me away from reaching my goal.  This is not a point however that has left me bitter as it would most I image, it has shown me that patience is in fact a virtue and taught me how to be very frugal.  Examples of house expenses that I mentioned earlier, halfway into high school my dad lost both his jobs and had to go back to school to which both my brother and I had to work a bit harder to help support the family. Occasionally my father would ask for a loan, or my mother would need money to sent to her family in Mexico, because my grandmother is quite old and my grandfather diseaced.
I often ask myself if I would trade my life for a more entitled one and the answer is always no.  I feel that the open-minded caring for the underprivileged hard working perspective I currently have is something that I wouldn't give the world to give up.  The struggles I have had and the decisions I have made have made me into a confident, respectful hardworking person and I looking back I think that my grade school experiences coupled with my experiences at rice have given me the global education one can only dream of.  

7)Expect questions concerning what you think about ethics and healthcare (e.g., abortion, cloning, euthanasia). How much thought and research you have put into the field of medicine and how you play a role in its future.
Ethics and healthcare. I have to say I have a large interest in the integration of technological advances and new ways of collecting data from a patient and presenting it to them in a way that they can understand.(Medical Chart Person) That can seem very controversial, depending on the interpretation.  Conservatively I look at the evolution of the medical chart, into something that becomes accessible to the patient.  Our society thanks to the increased consumption of information is becoming more informed about the way the environment affect their health and the actions they can take to change it.   

8)What are your hobbies? Interviewer wants to make sure you are a well rounded person.  Specify unique things about myself that the interviewer may want to hear.
As hobbies I enjoy learning how to code, watch ted talks on a variety of issues that range from sociology to advanced physics and back to philosophy.  I enjoy talking about ideas with people and learning how backeround influences outcome.  Much like malcolm gladwell did in his book Outliers.  On top of that I love watching tv and other movies with my friends while hanging out and eating whatever fast food we can get our hands on.  

9)What exposure have you had to the medical profession? whether or not you have had many medical experiences and whether or not those have impacted what type of physician you want to become??
I have not had a great deal of medical experiences but the one that I have had has been very enriching.  Last semester I was gifted a mentor from a scholarship foundation that works as a head pain nurse at Memorial Hermann.  As a result I was able to sign on as a volunteer in his department and visit on fridays when I had the time.  We would visit all of his patients who varied within the field of trauma usually from gang related activities to surgical pains.  We visited an anesthesiologist during surgery, and while he input a cathedar.  These experiences with the Daniel, gave me a great idea on what it meant to be a physician and I can happily say that it has given me pride to follow into the field.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Other Questions}
1) What will you do if you aren't accepted to medical school?
If I wasn't accepted into medical school I would pursue a Ph.D/MBA in bioengineering and work on developing biotechnologies. I am determined to get a Ph.D if i don't get into medical school, but having worked in a lab know that progress is slow and politics stressful in labs and I would like avoid those binds.  I would work as an engineer pushing for the development of technologies that are both affordable to third world countries and sustainable.  
 2)What makes you special??I very grounded and friendly.  I have had the great fortune to have been exposed to the diversity that exists and as a result repect all individuals for their beliefs and celebrate our difference. For this reason I find us all to be very interesting and enjoy having conversations with people similar or starkinly different from me.
3)What are three things you want to change about yourself?
I want to be more fiscally responsible, I want to learn how to make time to relax, and I want to work on my communication skills.
4)What do you think will be your greatest challenge in completing medical school or learning how to be a doctor??Hard time memorizing things. 
5)In your view, what is the most pressing problem facing medicine today?
The fact that there is a rising number of ?Rising cost of health care.  The rate at which we are currently discovering treatment and inventing medical equipment is great.  I don't have any quarrels with the production of new treatment, but our ability to preserve life and in some cases prolong it is to great for our country to handle at the moment.
6)If you could do anything different in your education, what would you do?
I would have done one of two things.  One I would have chosen a different field to go into or I would have joined the military and pursued a career in medicine through their track.  ?In a different field I probably would have studied computer science, physics, or math.  Perhaps pursued an mba and gone into business consulting or been an investment banker.  I could have opted in pursuing a phd in computer science to work on the hot field of robotics.  One of the things that definitely stopped me from pursuing these field is not having the proper training to succeed in them at Rice.  The Math, Physics and Computer Science department are very advanced places to be and with my small town public school education, I didn't have the theoretical background to be successful in the fields.  
I alway pictured myself going into the military for medicine because I enjoy having a regimented lifestyle and found it to be a very noble job.  I spoke to a recruiter, and talked to friends who were in the military and found it to be the life for me.  The only reason I didn't do it was because I received a full scholarship to Rice University and my parents were not too fond of the idea of me going into the military during a shooting war.

7)What do you do in your spare time??Service to the community, personal development, and relaxing. Its a very broad answer because it seems that  you can find me doing one of three things along those lines in almost all my free time. Im very big on giving presentations at my home town and in Houston, and am a big fan of providing people with the tools they need to succeed.  
How did you get here??Hard work. Seizing opportunities and a little luck. 

8)Why would you be a good doctor??I would be a great doctor because I will have a great interest in the wellbeing of my patients, working to provide primary healthcare at a reasonable price so that families will not be stricken by medical tragedies and fall into a poverty cycles.


10)What do you feel are the most important qualities in being a good doctor??A doctor must be caring and realize the impact that he may make with each life that he touches.

12)Are you a leader or a follower? Why??I am a great follower, but a leader in the absence of a leader.


14)Discuss your clinical experiences.?my clinical experiences have been few but enjoyable.  They have both been in trauma and I have seen a variety of the worst cases that physicians have to deal with.  

15)Discuss your volunteer work.?I love habitat for humanity and working at bike shops
What do you think you will like most about medicine??

16)Be prepared to discuss managed healthcare and changes in the US healthcare system.?
17)How are you a match for our medical school??I think I am perfect for this program because I could greatly benefit from the help that it offers.  there is only so much that self study can teach a persona and through this program  would have all the resources necessary to develop into a bread rice student.

18)Would you perform abortions as a doctor? Under what conditions??I would perform abortions as long as they were requested before the fetus is considered a human being.  

19)What do you think you will like least about medicine?
Insurance and the heavy dependence that distribution of care has on income.  
I hate the management of cost a necessary evil though it might be. Also one of the reasons I considered going into the military.  The biggest dread I have in medicine today is the idea of rejecting care because of a lack of insurance.  Mostly because I know that one of the reasons my family didn't go to the doctor very often is because we didn't have health insurance.  Seeing my parent face illnesses without the help of a doctor was painful to watch and I know that we were just one of the families that have to do that in order to stay within their budget.  I don't have a way to fix that yet but I will probably not shoot to be a high payed surgeon, as long as I can provide the care people need.  

20)How would you describe the relationship between science and medicine?
FDA now, but websites like 
Science is the means by which medical treatments are developed, improved, and perfected, but medicine itself is a service field focused on healing others with the resources available. I work in a matrix mechanics laboratory where we focus on studying the contributions the extracellular matrix makes to the physical properties of valve tissue to eventually engineer artificial heart valves to be used in transplants, though that technology in itself is very far away.  Science is what I see in the lab I work in.  Day in and day out designing and running experiments and collecting data in order to improve the treatments that can be offered in clinics.  Medicine is the art of using the information given to us by our training and by our individual observation as medical professional to improve the health of individuals in our care.  With the increasing speed of data collection, process and analystis, the line where science and medicine are different becomes very blurred.  I say that because it used to be that almost all data collected from clinical trials was collected by the FDA.  That is no longer true and it will continue to be less true as passing things through the FDA becomes unreasonable. Let me take a second to say that the process by which the FDA approves medicine is not dumb, but it is outdated and in the future I hope that we will look toward the use of resources like patientslikeme.com to collect data.  

Analogy: two man fire brigade.  Science grabs the water from the ocean and passes it to the second brigade man medicine so that he can pour it into the fire. 

21) Who has most influenced your life so far and why?
My father has been my biggest influence for two reasons; he is brave and hardworking.
Brave- Came to the United States with very little confidence of anything, with only a drive to live a better life.
Hardworking- My dad has always worked.  Always is almost an understatement.  He has worked 2-3 jobs his entire life, and got an associates degree at the age of 55 in order to be able to find a job.  



My father has influenced me most in my life because of the people I have met and known, I don't think I have found a harder working and loving person than my father.  He has gone through several jobs, several layoffs, and an associates degree at the age of 50 to provide for our family.  An thats just what I have been alive for.  Growing up he lived a hard life in Mexico without a father and had a lot of courage moving to the united states after marrying my mother so that we would have a good life.  He had no idea how it would work out.  He just had the courage to take a risk for the better and the work ethic to make it happen.  
From this I take courage in the challenges that I face in school, making them seem small in comparison and I look forward to the day in which I can provide my parents with the retirement they deserve for working so hard to raise me and my brothers and sisters.  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{}
\section{}
\subsection{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{}
\section{}
\subsection{}

\end{document}